Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

>>>>

In the case of other internal change factors other than IS1, all test results
with three significant values can be successfully detected and determined the source
the cause because the algorithm can determine that the CDF data latency case regression
has a different distribution with the CDF baseline latency data. While on
cases that simulate changes from external, i.e. cases ES1 to
ES4, PRA Engine can also detect the occurrence of regression but the results of critical analysis
path cannot determine the source of the regression because it does not
caused by changes in service level.

It can be concluded that the algorithm has not been able to determine whether the regression
occurs due to changes that occur at the application level or changes
that occur outside the application such as an increase in the number of users or an increase in
load on some operations. However, if the critical path analysis can be seen the difference
latency of operations that exceed a certain threshold can be an indication that
regression that occurs is caused by changes at the application level. On the other hand, if
critical path analysis cannot determine which operation is a candidate cause
regression because the difference is not greater than the threshold, it can be
indication that the detected regression is due to changes caused by
by external factors.
